---
title      : Titanic Survival Predictions
subtitle   : Coursera Project
author     : Nguyen Thanh Trung
framework  : io2012
highlighter: highlight.js
hitheme    : zenburn
mode: selfcontained
---

## About the product

Using the Titanic survival data available at **Kaggle** (https://www.kaggle.com/c/titanic-gettingStarted/data), 
we were able to build a prediction model was built. Based on your age, ticket class, gender and 
number of family members onboard, we can predict your chance of surviving the Titanic shipwreck.

A Titanic survival dataset contains
- Passenger's name, age, sex
- Ticket type, boarding location
- Whether he survives

---

## Titanic Data

```{r echo=F}
# Load the Titanic dataset
library(RCurl)
if (file.exists('train.csv')) { # The file is in local
    Titanic = read.csv('train.csv')
} else {
    url <- getURL('https://raw.githubusercontent.com/R-R-/CourseraDevelopingDataProduct/master/train.csv')
    Titanic = read.csv(text = url)
}
goodColumnsNoLabel <- c("Pclass", "Sex", "Age", "Parch")
goodColumns <- c("Survived", goodColumnsNoLabel)
Titanic <- Titanic[, goodColumns]
str(Titanic)
```

---

## Building prediction model

Based on the data, a simple prediction model was built.

```{r, eval=FALSE}
goodColumnsNoLabel <- c("Pclass", "Sex", "Age", "Parch")
goodColumns <- c("Survived", goodColumnsNoLabel)
Titanic <- Titanic[, goodColumns]
Titanic$Pclass <- factor(Titanic$Pclass)
Titanic$Survived <- factor(Titanic$Survived)
Titanic$Parch <- factor(Titanic$Parch)
modelFit <- train(Survived ~ ., data = Titanic, method = "glm")
```

---

## Final product

The final product was made available online at: https://thanhtnguyen.shinyapps.io/Coursera/

User can select their own scenario, including:

1. Age
2. Gender
3. Ticket type
4. Number of family members onboard

and our server will make predictions for them. The result will then 
be displayed in a user friendly manner to the user.
